Titulo

### 2014-10-27 RotacionOutFlows/Paper/ms.tex
little change

---------------------------------------------------------------------\\
MISSING: What has been done related to this? (In the astronomy world)\\
-----------------------------------------------------------------------\\

As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum. The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation. The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle. What happens is that photons are emmited from the an homogeneus distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\

>>>>

---------------------------------------------------------------------\\
MISSING: What has been done related to this?\\
-----------------------------------------------------------------------\\

As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum. The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation. The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle. What happens is that photons are emmited from a central distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
